Social inequality in mortality among adults and elderly in northern Sweden 1851--2013\footnote{Paper presented at the session 'Health and Mortality in Arctic Populations'. The Ninth International Congress on Arctic Social Sciences, Umeå, June 8--12, 2017}

### 2017-06-02 icass.Rnw
new acknowledgement

This work was undertaken within the Centre for Demographic and Ageing
Research (CEDAR) at Umeå University and with support from the Swedish
Research Council (VR) (grant No. 421-2012-892) and the project 
\emph{Old age, health, and inequality: Mortality from a life course perspective in Sweden 1986--2009}, 
 financed by the Swedish Research Council (grant No. 421-2012-892). We thank The Demographic Data
Base for giving us access to data and Jonas Helgertz, Department of
Economic History, Lund University, for providing us with scripts for
creating {\sc Hisclass} from Swedish Census data.

>>>>

This work was undertaken within the research program \emph{Ageing and Living Conditions} at the Centre for Demographic and Ageing Research (CEDAR) at Umeå University, financed by the Swedish Research Council (grant No 349-2008-6592) and the project \emph{Old age, health and inequality: Mortality from a life course perspective in Sweden 1986--2009}, financed by the Swedish Research Council (grant No 421-2012-892). We thank the Demographic Data Base, Umeå University, for giving us access to data and Jonas Helgertz, Department of Economic History, Lund University, for providing us with scripts for creating {\sc Hisclass} from Swedish Census data.
